\sys: Light-touch Data-Parallel Shell Processing

### 2020-05-18 pldi/draft.tex
Distributability -> Parallelizability

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
  Distributed systems offer notable benefits over centralized ones.
  Reaping these benefits, however, requires programming in a way that makes distribution explicit---\eg via new programming languages, distributed frameworks, or source-level annotations.
  This paper presents \sys, a shell variant that automatically and correctly scales out \unix shell pipelines. 
  Its insight is that pipelines already express stream computations that can be automatically distributed.
  To distribute them, \sys
    decomposes primitives into distributability classes,
    identifies high-distributability stages,
    applies rewriting rules for largest possible subprograms,
    and orchestrates their execution.
Experiments with complex pipelines show substantial speedups and the ability to operate on large input datasets, all without any developer input.
\end{abstract}

% Its runtime component provides orchestration and planning support during the execution of the program.
% These are from the abstract:
%  with regards to the sequential program.
  % leveraging the insight that such programs already express stream computations, with their stages falling under a few, known distributability classes.
% a series of techniques for automatically 
% 
% Key challenges include 
% surprisingly expressive, 
% maximally distributable subprograms
%

@@

The paper is structured as follows.
It starts by introducing the necessary background on shell scripting and overviewing \sys~\sx{bg}.
Sections \ref{distributability}--\ref{impl} highlight key contributions:
\begin{itemize}
  \item
  \S\ref{distributability}
    studies the parallelizability of a large set of shell commands and introduces a lightweight annotation language for commands that can be executed in a data-parallel manner.

@@

%% \kk{Begin of new intro sketch}
%% \begin{itemize}
%% \item Why is parallelism important (especially in the context of data
%%   processing). Significant performance benefits as most computer
%%   systems today have multiple processors that are under utilized
%% \item (Similarly to how it is now) unfortunately, it is quite hard
%%   reaping these benefits in contrast to sequential data
%%   processing. [Show Bash pipeline].
%% \item To benefit from parallelism, the current options are
%%   extreme. Either very fine-grained and low level (parallelism using
%%   fine-grained C libraries) for maximum performance, or very coarse
%%   grained and bulky where one has to use a proper big-data
%%   framework. (Can we fit the shell ones here (gnu-parallel, etc))
%% \item The common thing is that one needs to rewrite big part of their
%%   application, often requiring expertise and redesigning its
%%   architecture, in order to get benefits that in the end might not
%%   explain the cost.
%% \item To address this issue, we propose Dish, a thin layer that
%%   automatically! parallelizes a given shell script. Key insight is
%%   that a large subset of the shell language can be encoded in a
%%   dataflow graph model, a flexible representation that allows for
%%   parallelization optimizations.
%% \end{itemize}
%% Contributions:
%% \begin{itemize}
%% \item Study of the shell primitives, identification of
%%   families/classes of commands that share
%%   distributability/parallelization properties, and a classification of
%%   coreutils/POSIX commands in these distributability properties.
%% \item Dataflow graph model that is suitable for the shell
%% \item A set of optimizations on this model that can be thought of as
%%   rewriting rules on the dataflow graph, that are sound and exploit
%%   parallelism.
%% \end{itemize}
%% \kk{End of new intro sketch}

@@

%% \begin{figure}[t]
%% \centering
%% \includegraphics[width=0.49\textwidth]{\detokenize{./figs/dish_overview.pdf}}
%% \caption{
%%   \textbf{High-level schematic.}
%%   \sys leverages distributability analysis for built-in commands and any developer extensions (left) to automatically transform shell scripts (mid) and orchestrates their
%%   execution (right).
%% }
%% \vspace{-10pt}
%% \label{fig:schematic}
%% \end{figure}

@@

%% To answer this question we develop \sys, a shell variant that transforms traditional \unix pipelines into their distributed equivalents, enabling \emph{distribution-oblivious programming}.
%% The key insight behind \sys is that a large part of the shell language can be encoded in a distributed dataflow graph model, providing structure to distribute computations.
%% %% \kk{Replaced that: the language of the Unix shell already encodes stream processing, providing most of the information required to distribute a computation. }
%% % FIXME \kk{I am not sure whether stream processing provides information for distributing a computation on its own. Maybe we can say that the shell exposes operator level parallelism, and that this is the first step to distributing a computation}.
%% \sys builds on this insight with a careful study of the distributability properties of shell primitives and commands, a definition of a dataflow graph model that is suitable for the shell, a set of parallelization optimizations that preserve the behaviour of the graph, and a late-bound command-prefixing scheme for deferring scheduling decisions to the distributed planner (\ie when runtime information is available).
%% A \sys-enabled $p_1$ will run \ttt{tr}s on parallel streams,
%%   use a mostly-parallel tree of \ttt{sort}s,
%%   run \ttt{uniq} mostly in parallel,
%%   execute \ttt{head} in one of the streams,
%%   and (trivially) merge streams in \ttt{out}.

@@

%% The combination of automated transformations for program distribution with the ability to maintain correct non-distributed semantics results in several benefits.
%% % \sys converts legacy shell pipelines into their distributed equivalents fully automatically, offering $100\times$ improvements in performance without a single line of additional code or annotation.
%% First, shell users composing pipelines (or simply running legacy pipelines on massive datasets) can see scalability benefits without any manual effort---no need for \ttt{qsub}~\cite{gentzsch2001sun}, \textsc{SLURM}~\cite{yoo2003slurm}, calls to \textsc{GNU} \ttt{parallel}~\cite{Tange2011a}, or any manual rewriting~\cite{mapreduce:08, ciel:11, spark:12}.
%% Second, developers of new shell commands can use a lightweight domain-specific language to express their distributability properties rather than ad-hoc, command-specific flags such as {\tt -t},  {\tt NUM\_THREADS}, \ttt{-t}, \ttt{-p} \etc
%% Most importantly, \sys provides an architectural lesson for system designers---namely, that large-scale efforts in the distributed- and operating-system literature to provide a \unix-like distributed equivalent~\cite{ousterhout1988sprite, mullender1990amoeba, pike1990plan9, barak1998mosix} would have been simplified by a thin (but sophisticated) rewriting shim like the one \sys provides.
%% % Nice critique on parallel: https://bugs.debian.org/cgi-bin/bugreport.cgi?bug=597050#75

@@

%% The paper is structured as follows.
%% It starts by introducing the necessary background on shell scripting and overviewing \sys~\sx{bg}.
%% Sections \ref{distributability}--\ref{impl} highlight key
%% contributions:
%% \begin{itemize}

%%   \item
%%   \S\ref{distributability} studies several distributability classes and introduces the distributability characterization language.

@@

The next few sections (\S\ref{distributability}--\ref{impl}) discuss \sys's design and implementation details.
% They also outline other, less obvious challenges---such as the synchronization of environment variables, distributed file operation, \etc.

\section{Distributability Classes}
\label{distributability}

@@

To have any hope of distributing pipelines, \sys first needs to understand the distribution characteristics of their individual commands.
This understanding is encoded in a command's \emph{distributability} class.
Informally, a distributability class represents the level of synchronization required by copies of a command that execute in parallel.
It focuses on capturing characteristics that are important for distribution, rather than the entire the observable behavior of a command.
\sys leans towards having a few coarse classes rather than many detailed ones---among other reasons, to simplify their understanding and use by command developers.
% Make the connections that this is like a type, that doesn't capture everything, but is good-enough

This section starts by defining these classes, along with a distributability study of the commands found in standard libraries such as {\sc POSIX} and GNU Coreutils~\sx{cmd}.
Building on this study, it develops a DSL that enables command classification by its developers~\sx{ext}.
In return, \sys uses this DSL to tag commands in the standard libraries and generate their wrappers, as presented in later sections.

\subsection{Distributability of Standard Libraries}
\label{cmd}

@@

\begin{table}[t]
\center
\footnotesize
\setlength\tabcolsep{3pt}
\caption{
  \footnotesize{
    \textbf{Distributability Classes}.
    Broadly, \unix commands can be broken down into to five classes.
  }
}
\begin{tabular}{l @{\extracolsep{\fill}} lll}
\toprule
Class                           &  Key    & Example Commands                            & Coreutils       \\ % & POSIX       \\
\midrule
Stateless                       & ~\tsta  & \tti{tr},   \tti{cat},    \tti{grep}        &  22 (21.1\%)    \\ %  &           \\  % 22
Pure                            & ~\tpur  & \tti{sort}, \tti{wc},     \tti{uniq}        &  21 (20.1\%)    \\ %  &           \\  % 21
(Distr.) File-System~           & ~\tdfs  & \tti{cp},   \tti{ln},     \tti{rm}          &  27 (25.9\%)    \\ %  &           \\  % 27
Side-effectful                  & ~\tsid  & \tti{env},  \tti{chroot}, \tti{whoami}      &  25 (24\%)      \\ %  &           \\  % 25
Irreversible                    & ~\tirr  & \tti{exit}, \tti{lpr},    \tti{reboot}      &  5  (0.4\%)     \\ %  &           \\  % 5
% \midrule
% Shell PL Constructs             &                         &                  \\
% \etc                            &                         &                  \\
\bottomrule
\end{tabular}
\label{tab:classes}
\end{table}

@@

\paragraph{Pure Commands}
The second class contains pure commands \pur.
These commands respect functional purity---re\-turn\-ing the same results for the same inputs---but maintain internal state across their entire pass.
The details of this state and its propagation during piecewise element processing affect their distributability characteristics.

@@

    <command-list> ::= <command>
    \alt <command> <command-list>
  \end{grammar}
  \caption{
\textbf{Distributability description language.}
The DSL captures important information regarding the distributability of a command.
\vspace{-10pt}
}
  \label{fig:dsl}
\end{figure}
}

%% \paragraph{Command Inputs and Outputs}
%% A second concern captured by the AL is the order of inputs and outputs.
%% Commands generally read multiple input streams (and, at cases, write to multiple output streams).
%% The invariants between inputs and outputs must be maintained over the distributed execution of the program.
%% % but these maintain different invariants, enabling very different distributability characteristics.

@@

% As mentioned in distributability, pure commands can be broken down
% into different categories. We might be able to get ideas about this
% from this paper:
% \url{http://www.cs.toronto.edu/~azadeh/papers/pldi17-ex.pdf} and its
% continuation in PLDI 2019.
% FIXME: \nv{Cite this paper?}
\tr{Can we find a solution for the commands in coreutils?}

@@

%% Finally, whenever the algorithm encounters a command, it first
%% checks whether it is safe to parallelize it. A command is considered
%% safe for parallelization if (i) it belongs to the \sta or \pur distributability classes, and (ii) does not read from a read-once file (such as a pipe containing configuration data) as parallelization would break this. % why couldn't we replicate this?
%% If the command is safe, \sys creates a node containing that command  and adds it to a singleton dataflow graph.
%% If the command is unsafe, it is still added to the dataflow graph, but is not further parallelized by the optimizer.

@@

\heading{Performance}
% TODO \nv{Need to change terminology in plots---files should be (attempted) parallelism, name benchmark, cat should be merge.}
Fig.~\ref{fig:microbenchmarks} presents the speedup gained by \sys as a function of the level of parallelism (1--200$\times$).
% we experiment with a $200\times$ level of parallelism to see potential overheads
Each one of these plots reports on three different configurations:
  (i) distributed, which captures only the runtime of the distributed computation,
  (ii) +compile, which adds the \sys' analysis and generation overhead, and
  (iii) +merge, which adds a final merger  gathering the results at the end of the pipeline.
Parallelism of 200$\times$ was explicitly chosen to show the \sys-internal overheads on suboptimal configurations;
  \sys itself would never attempt a factor that is above the number of available compute nodes.
The results show significant speedups, ranging between 4--70$\times$, depending on the distributability characteristics of individual pipelines.

@@

\paragraph{Cluster Computing}
Modern analytics frameworks~\cite{mapreduce:08, ciel:11, spark:12,
  naiad:13} and domain-specific languages~\cite{alvaro2011consistency,
  distal:13, meiklejohn2015lasp} go a step further in terms of
automation by providing a few carefully-designed primitives.  These
primitives make strong assumptions about the nature of the
computation---\eg strongly-eventual commutative functions that can
proceed in parallel.  By targeting specific classes of computation
(\emph{viz.} \sys's distributability), they render distributed
computation efficiently.

@@

\paragraph{Annotation-based Distribution}
Recent systems on light-touch distribution, such as
Ignis~\cite{ignis:19} and Mozart~\cite{mozart:19}, are more general
than cluster-computing frameworks.  They also lower (but not entirely
eliminate) developer effort by automating most of the rewriting
process.
% Both work on high-level, managed languages---server-side JavaScript for Ignis and Python for Mozart---that allow runtime transformations without affecting the broader environment under which a program executes.
For the critical points where user input is required, they provide a
high-level declarative DSL with varying (but limited) degrees of
expressive power.
% Annotations are used by ---complicated by the use of third-party
% libraries similar to \sys's extensions.
Unfortunately, a challenge with this approach is that users composing
applications by using third-party libraries do not understand their
distributability details well-enough to annotate them.

@@

\paragraph{Future Work}
% \label{limitation}
% \item No cycles (multiple commands writing and reading from the same file)
There are several worthwhile directions for future work.  One
direction would be an extension of the distributability analysis of
\sys, in order to guide it using dynamic information. This could
enable a formal study of the analysis~\sx{impl} to show that it
returns regions that are safe to distribute.  Recent work on
formalizing the semantics of the POSIX shell~\cite{smoosh:20} make
such an attempt possible.

@@

\paragraph{Conclusion}
This paper presented \sys, a shell variant that automatically and correctly scales out distribution-oblivious shell pipelines. 
\sys's insight is that shell pipelines already express streaming computations that can be automatically distributed.
To achieve its goal, \sys
  decomposes primitives into distributability classes,
  identifies high-distributability stages,
  applies rewriting rules for largest possible subprograms,
  and orchestrates the execution of the distributed program.
% Its runtime component provides orchestration and planning support during the execution of the program.
Experiments with complex pipelines show substantial speedups and the ability to operate on large input datasets, all without any developer input.

\section*{Acknowledgments}

>>>>

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
  Distributed systems offer notable benefits over centralized ones.
  Reaping these benefits, however, requires programming in a way that makes distribution explicit---\eg via new programming languages, distributed frameworks, or source-level annotations.
  This paper presents \sys, a shell variant that automatically and correctly scales out \unix shell pipelines. 
  Its insight is that pipelines already express stream computations that can be automatically distributed.
  To distribute them, \sys
    decomposes primitives into parallelizability classes,
    identifies high-parallelizability stages,
    applies rewriting rules for largest possible subprograms,
    and orchestrates their execution.
Experiments with complex pipelines show substantial speedups and the ability to operate on large input datasets, all without any developer input.
\end{abstract}

% Its runtime component provides orchestration and planning support during the execution of the program.
% These are from the abstract:
%  with regards to the sequential program.
  % leveraging the insight that such programs already express stream computations, with their stages falling under a few, known parallelizability classes.
% a series of techniques for automatically 
% 
% Key challenges include 
% surprisingly expressive, 
% maximally distributable subprograms
%

@@

The paper is structured as follows.
It starts by introducing the necessary background on shell scripting and overviewing \sys~\sx{bg}.
Sections \ref{parallelizability}--\ref{impl} highlight key contributions:
\begin{itemize}
  \item
  \S\ref{parallelizability}
    studies the parallelizability of a large set of shell commands and introduces a lightweight annotation language for commands that can be executed in a data-parallel manner.

@@

%% \kk{Begin of new intro sketch}
%% \begin{itemize}
%% \item Why is parallelism important (especially in the context of data
%%   processing). Significant performance benefits as most computer
%%   systems today have multiple processors that are under utilized
%% \item (Similarly to how it is now) unfortunately, it is quite hard
%%   reaping these benefits in contrast to sequential data
%%   processing. [Show Bash pipeline].
%% \item To benefit from parallelism, the current options are
%%   extreme. Either very fine-grained and low level (parallelism using
%%   fine-grained C libraries) for maximum performance, or very coarse
%%   grained and bulky where one has to use a proper big-data
%%   framework. (Can we fit the shell ones here (gnu-parallel, etc))
%% \item The common thing is that one needs to rewrite big part of their
%%   application, often requiring expertise and redesigning its
%%   architecture, in order to get benefits that in the end might not
%%   explain the cost.
%% \item To address this issue, we propose Dish, a thin layer that
%%   automatically! parallelizes a given shell script. Key insight is
%%   that a large subset of the shell language can be encoded in a
%%   dataflow graph model, a flexible representation that allows for
%%   parallelization optimizations.
%% \end{itemize}
%% Contributions:
%% \begin{itemize}
%% \item Study of the shell primitives, identification of
%%   families/classes of commands that share
%%   parallelizability/parallelization properties, and a classification of
%%   coreutils/POSIX commands in these parallelizability properties.
%% \item Dataflow graph model that is suitable for the shell
%% \item A set of optimizations on this model that can be thought of as
%%   rewriting rules on the dataflow graph, that are sound and exploit
%%   parallelism.
%% \end{itemize}
%% \kk{End of new intro sketch}

@@

%% \begin{figure}[t]
%% \centering
%% \includegraphics[width=0.49\textwidth]{\detokenize{./figs/dish_overview.pdf}}
%% \caption{
%%   \textbf{High-level schematic.}
%%   \sys leverages parallelizability analysis for built-in commands and any developer extensions (left) to automatically transform shell scripts (mid) and orchestrates their
%%   execution (right).
%% }
%% \vspace{-10pt}
%% \label{fig:schematic}
%% \end{figure}

@@

%% To answer this question we develop \sys, a shell variant that transforms traditional \unix pipelines into their distributed equivalents, enabling \emph{distribution-oblivious programming}.
%% The key insight behind \sys is that a large part of the shell language can be encoded in a distributed dataflow graph model, providing structure to distribute computations.
%% %% \kk{Replaced that: the language of the Unix shell already encodes stream processing, providing most of the information required to distribute a computation. }
%% % FIXME \kk{I am not sure whether stream processing provides information for distributing a computation on its own. Maybe we can say that the shell exposes operator level parallelism, and that this is the first step to distributing a computation}.
%% \sys builds on this insight with a careful study of the parallelizability properties of shell primitives and commands, a definition of a dataflow graph model that is suitable for the shell, a set of parallelization optimizations that preserve the behaviour of the graph, and a late-bound command-prefixing scheme for deferring scheduling decisions to the distributed planner (\ie when runtime information is available).
%% A \sys-enabled $p_1$ will run \ttt{tr}s on parallel streams,
%%   use a mostly-parallel tree of \ttt{sort}s,
%%   run \ttt{uniq} mostly in parallel,
%%   execute \ttt{head} in one of the streams,
%%   and (trivially) merge streams in \ttt{out}.

@@

%% The combination of automated transformations for program distribution with the ability to maintain correct non-distributed semantics results in several benefits.
%% % \sys converts legacy shell pipelines into their distributed equivalents fully automatically, offering $100\times$ improvements in performance without a single line of additional code or annotation.
%% First, shell users composing pipelines (or simply running legacy pipelines on massive datasets) can see scalability benefits without any manual effort---no need for \ttt{qsub}~\cite{gentzsch2001sun}, \textsc{SLURM}~\cite{yoo2003slurm}, calls to \textsc{GNU} \ttt{parallel}~\cite{Tange2011a}, or any manual rewriting~\cite{mapreduce:08, ciel:11, spark:12}.
%% Second, developers of new shell commands can use a lightweight domain-specific language to express their parallelizability properties rather than ad-hoc, command-specific flags such as {\tt -t},  {\tt NUM\_THREADS}, \ttt{-t}, \ttt{-p} \etc
%% Most importantly, \sys provides an architectural lesson for system designers---namely, that large-scale efforts in the distributed- and operating-system literature to provide a \unix-like distributed equivalent~\cite{ousterhout1988sprite, mullender1990amoeba, pike1990plan9, barak1998mosix} would have been simplified by a thin (but sophisticated) rewriting shim like the one \sys provides.
%% % Nice critique on parallel: https://bugs.debian.org/cgi-bin/bugreport.cgi?bug=597050#75

@@

%% The paper is structured as follows.
%% It starts by introducing the necessary background on shell scripting and overviewing \sys~\sx{bg}.
%% Sections \ref{parallelizability}--\ref{impl} highlight key
%% contributions:
%% \begin{itemize}

%%   \item
%%   \S\ref{parallelizability} studies several parallelizability classes and introduces the parallelizability characterization language.

@@

The next few sections (\S\ref{parallelizability}--\ref{impl}) discuss \sys's design and implementation details.
% They also outline other, less obvious challenges---such as the synchronization of environment variables, distributed file operation, \etc.

\section{Parallelizability Classes}
\label{parallelizability}

@@

To have any hope of distributing pipelines, \sys first needs to understand the distribution characteristics of their individual commands.
This understanding is encoded in a command's \emph{parallelizability} class.
Informally, a parallelizability class represents the level of synchronization required by copies of a command that execute in parallel.
It focuses on capturing characteristics that are important for distribution, rather than the entire the observable behavior of a command.
\sys leans towards having a few coarse classes rather than many detailed ones---among other reasons, to simplify their understanding and use by command developers.
% Make the connections that this is like a type, that doesn't capture everything, but is good-enough

This section starts by defining these classes, along with a parallelizability study of the commands found in standard libraries such as {\sc POSIX} and GNU Coreutils~\sx{cmd}.
Building on this study, it develops a DSL that enables command classification by its developers~\sx{ext}.
In return, \sys uses this DSL to tag commands in the standard libraries and generate their wrappers, as presented in later sections.

\subsection{Parallelizability of Standard Libraries}
\label{cmd}

@@

\begin{table}[t]
\center
\footnotesize
\setlength\tabcolsep{3pt}
\caption{
  \footnotesize{
    \textbf{Parallelizability Classes}.
    Broadly, \unix commands can be broken down into to five classes.
  }
}
\begin{tabular}{l @{\extracolsep{\fill}} lll}
\toprule
Class                           &  Key    & Example Commands                            & Coreutils       \\ % & POSIX       \\
\midrule
Stateless                       & ~\tsta  & \tti{tr},   \tti{cat},    \tti{grep}        &  22 (21.1\%)    \\ %  &           \\  % 22
Pure                            & ~\tpur  & \tti{sort}, \tti{wc},     \tti{uniq}        &  21 (20.1\%)    \\ %  &           \\  % 21
(Distr.) File-System~           & ~\tdfs  & \tti{cp},   \tti{ln},     \tti{rm}          &  27 (25.9\%)    \\ %  &           \\  % 27
Side-effectful                  & ~\tsid  & \tti{env},  \tti{chroot}, \tti{whoami}      &  25 (24\%)      \\ %  &           \\  % 25
Irreversible                    & ~\tirr  & \tti{exit}, \tti{lpr},    \tti{reboot}      &  5  (0.4\%)     \\ %  &           \\  % 5
% \midrule
% Shell PL Constructs             &                         &                  \\
% \etc                            &                         &                  \\
\bottomrule
\end{tabular}
\label{tab:classes}
\end{table}

@@

\paragraph{Pure Commands}
The second class contains pure commands \pur.
These commands respect functional purity---re\-turn\-ing the same results for the same inputs---but maintain internal state across their entire pass.
The details of this state and its propagation during piecewise element processing affect their parallelizability characteristics.

@@

    <command-list> ::= <command>
    \alt <command> <command-list>
  \end{grammar}
  \caption{
\textbf{Parallelizability description language.}
The DSL captures important information regarding the parallelizability of a command.
\vspace{-10pt}
}
  \label{fig:dsl}
\end{figure}
}

%% \paragraph{Command Inputs and Outputs}
%% A second concern captured by the AL is the order of inputs and outputs.
%% Commands generally read multiple input streams (and, at cases, write to multiple output streams).
%% The invariants between inputs and outputs must be maintained over the distributed execution of the program.
%% % but these maintain different invariants, enabling very different parallelizability characteristics.

@@

% As mentioned in parallelizability, pure commands can be broken down
% into different categories. We might be able to get ideas about this
% from this paper:
% \url{http://www.cs.toronto.edu/~azadeh/papers/pldi17-ex.pdf} and its
% continuation in PLDI 2019.
% FIXME: \nv{Cite this paper?}
\tr{Can we find a solution for the commands in coreutils?}

@@

%% Finally, whenever the algorithm encounters a command, it first
%% checks whether it is safe to parallelize it. A command is considered
%% safe for parallelization if (i) it belongs to the \sta or \pur parallelizability classes, and (ii) does not read from a read-once file (such as a pipe containing configuration data) as parallelization would break this. % why couldn't we replicate this?
%% If the command is safe, \sys creates a node containing that command  and adds it to a singleton dataflow graph.
%% If the command is unsafe, it is still added to the dataflow graph, but is not further parallelized by the optimizer.

@@

\heading{Performance}
% TODO \nv{Need to change terminology in plots---files should be (attempted) parallelism, name benchmark, cat should be merge.}
Fig.~\ref{fig:microbenchmarks} presents the speedup gained by \sys as a function of the level of parallelism (1--200$\times$).
% we experiment with a $200\times$ level of parallelism to see potential overheads
Each one of these plots reports on three different configurations:
  (i) distributed, which captures only the runtime of the distributed computation,
  (ii) +compile, which adds the \sys' analysis and generation overhead, and
  (iii) +merge, which adds a final merger  gathering the results at the end of the pipeline.
Parallelism of 200$\times$ was explicitly chosen to show the \sys-internal overheads on suboptimal configurations;
  \sys itself would never attempt a factor that is above the number of available compute nodes.
The results show significant speedups, ranging between 4--70$\times$, depending on the parallelizability characteristics of individual pipelines.

@@

\paragraph{Cluster Computing}
Modern analytics frameworks~\cite{mapreduce:08, ciel:11, spark:12,
  naiad:13} and domain-specific languages~\cite{alvaro2011consistency,
  distal:13, meiklejohn2015lasp} go a step further in terms of
automation by providing a few carefully-designed primitives.  These
primitives make strong assumptions about the nature of the
computation---\eg strongly-eventual commutative functions that can
proceed in parallel.  By targeting specific classes of computation
(\emph{viz.} \sys's parallelizability), they render distributed
computation efficiently.

@@

\paragraph{Annotation-based Distribution}
Recent systems on light-touch distribution, such as
Ignis~\cite{ignis:19} and Mozart~\cite{mozart:19}, are more general
than cluster-computing frameworks.  They also lower (but not entirely
eliminate) developer effort by automating most of the rewriting
process.
% Both work on high-level, managed languages---server-side JavaScript for Ignis and Python for Mozart---that allow runtime transformations without affecting the broader environment under which a program executes.
For the critical points where user input is required, they provide a
high-level declarative DSL with varying (but limited) degrees of
expressive power.
% Annotations are used by ---complicated by the use of third-party
% libraries similar to \sys's extensions.
Unfortunately, a challenge with this approach is that users composing
applications by using third-party libraries do not understand their
parallelizability details well-enough to annotate them.

@@

\paragraph{Future Work}
% \label{limitation}
% \item No cycles (multiple commands writing and reading from the same file)
There are several worthwhile directions for future work.  One
direction would be an extension of the parallelizability analysis of
\sys, in order to guide it using dynamic information. This could
enable a formal study of the analysis~\sx{impl} to show that it
returns regions that are safe to distribute.  Recent work on
formalizing the semantics of the POSIX shell~\cite{smoosh:20} make
such an attempt possible.

@@

\paragraph{Conclusion}
This paper presented \sys, a shell variant that automatically and correctly scales out distribution-oblivious shell pipelines. 
\sys's insight is that shell pipelines already express streaming computations that can be automatically distributed.
To achieve its goal, \sys
  decomposes primitives into parallelizability classes,
  identifies high-parallelizability stages,
  applies rewriting rules for largest possible subprograms,
  and orchestrates the execution of the distributed program.
% Its runtime component provides orchestration and planning support during the execution of the program.
Experiments with complex pipelines show substantial speedups and the ability to operate on large input datasets, all without any developer input.
